Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-05 tex/VHzQ.tex
VHzQ.tex update

>>>>

\begin{figure*}
    \centering
    \subfigure[]{\includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/UHS_J0439+1634.png}} 
    \subfigure[]{\includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}} 
    \subfigure[]{\includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1443+3623.png}}
    \subfigure[]{\includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1623+4705.png}}
    \caption{(a) UHS J0439+1634 
                 (b) SDSS J0100+280 
               (c) SDSS J1443+3623 
 (d) SDSS J1623+4705
}
    \label{fig:foobar}
\end{figure*}
\subsubsection{Individual VH$z$Qs with Interesting MIR properties}
